---
title: "metSampler"
author: "Felipe de Jesus Muñoz González, Francisco Romero, Mirna Vazquez, Patricia Carvajal"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{metSampler}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction to _metSampler_ package

_metSampler_ Takes a two k-cones from the package Dycon that represent two different null spaces from a metabolic constraint based model and generates box plot graphics of the results.

The package cosists of three modules. The first module, samples two different null spaces from a metabolic constraint based model. This is accomplished through the Hit and Run algorithm (Hit and Run Cran package). The second module tests for diferences in distribution within the two different null spaces for each enzime. This test is performed through the Kolmogorov Smirnov test, the threshold on the p-value for accepting or rejecting the H0 is set to p=0.01. The last module generates a box plot for each of the null space enzimes.

# Installing _metSampler_ package

_metSampler_ Automatically will load its dependencies. 


```{r setup, include = FALSE, eval=FALSE}
install.packages("metSampler")
```

```{r load}
library(metSampler)
```

# Runing first module of _metSampler_ package

In this example to run the first module we will create to matrix and used to run sampler module.  

```{r}
A <- rbind(c(1,0), c(0,1), c(-1,0), c(0,-1))
B <- c(1, 1, 0, 0)
init.sampler(t(A),B)
```

# Runing second module of _metSampler_ package

In this example we run second module which will performe the distribution comparition of each enzime.

```{r, eval=FALSE}
distribution_results_distintos(Matriz1, Matriz2)
distribution_results_iguales(Matriz1, Matriz2)
```





